
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 180,
  fig.width = 8,
  fig.height = 5
)
```

# hubnR

<!-- badges: start -->
<!-- badges: end -->

R Package Containing Utility Functions And Themes For Personal Use

This Package contains:  

- Custom Themes  
- Custom Color Palettes  
- Helper Functions  
- Helper to save Plots with Custom Theme  


## Installation

Install development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("maxhuebner/hubnR")
```

## Load and Setup

This is a basic example which shows you how to solve a common problem:

```{r setup, message = 1:10}
library(hubnR)
setup_font_use() #To Load Font
```

## Theme Example

Here is a plot without using the Theme:  

```{r standard theme}
mtcars %>%
  ggplot(aes(mpg, cyl, color = as_factor(gear))) +
  geom_point() +
  labs(title = "title", subtitle = "Testing Subtitle")
```

Plot using HubnR-Theme:  

```{r hubnr theme}
mtcars %>%
  ggplot(aes(mpg, cyl, color = as_factor(gear))) +
  geom_point() +
  labs(title = "title", subtitle = "Testing Subtitle") + 
  theme_hubnr()
```

